Multi-resolution Neural Field Estimation

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
not sure about all the millions of refs in the conlclusion

 \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.

%  \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}

>>>>

 \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}. \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}\mike{While I love this kind of thing for a review, I'm not sure we have space for this kind of thing? Also it's not terribly specific.}
